\null\vfill
\begin{flushleft}
\thispagestyle{empty}
Indiana University Bloomington Libraries Publishing\\
1320 E. Tenth Street\\
Bloomington, IN 47405
\vspace{5mm}

© 2024 Curtis M. Lively\\
Illustrations © 2024 Zoe Michelle Dinges

\vspace{4mm}
\ccby

\textit{Through the Looking Glass: I. Why Cross-Fertilize?} © 2024 by Curtis M. Lively and Zoe Michelle Dinges is licensed under Attribution 4.0 International. To view a copy of this license, visit \url{http://creativecommons.org/licenses/by/4.0/}

\vspace{3mm}

\textbf{You are free to:}
\begin{itemize}
\tightlist
\item
  \textbf{Share---}copy and redistribute the material in any medium or format for any purpose, even commercially.\\
\item
  \textbf{Adapt---}remix, transform, and build upon the material for any purpose, even commercially.
\end{itemize}

The licensor cannot revoke these freedoms as long as you follow the license terms.

\vspace{3mm}

\textbf{Under the following terms:}
\begin{itemize}
\tightlist
\item
  \textbf{Attribution---}You must give
  \href{https://creativecommons.org/licenses/by/4.0/\#ref-appropriate-credit}{appropriate credit}, provide a link to the license, and
  \href{https://creativecommons.org/licenses/by/4.0/\#ref-indicate-changes}{indicate if changes were made}. You may do so in any reasonable manner, but not in any way that suggests the licensor endorses you or your use.\\
\item
  \textbf{No additional restrictions---}You may not apply legal terms or
  \href{https://creativecommons.org/licenses/by/4.0/\#ref-technological-measures}{technological measures} that legally restrict others from doing anything the license permits.
\end{itemize}

\textbf{Notices:}

\begin{itemize}
\tightlist
\item
  You do not have to comply with the license for elements of the material in the public domain or where your use is permitted by an applicable
  \href{https://creativecommons.org/licenses/by/4.0/\#ref-exception-or-limitation}{exception or limitation}.\\
\item
  No warranties are given. The license may not give you all of the permissions necessary for your intended use. For example, other rights such as
  \href{https://creativecommons.org/licenses/by/4.0/\#ref-publicity-privacy-or-moral-rights}{publicity, privacy, or moral rights} may limit how you use the material.
\end{itemize}

\vspace{5mm}
DOI: \href{https://doi.org/10.5967/gbd3-ka07}{10.5967/gbd3-ka07}
\end{flushleft}
